---
title: "Introgression Analysis"
author: "Jinliang Yang"
date: "Jan. 5th, 2015"
output: rmarkdown::tufte_handout
---

# SUMMARY
Test whether Totontepec maize lines have admixture with _mexicana_ using SNP50k data.   

---------

# Get genetic and physical map of the SNP50k

I compared the SNP50k map from Matt's archive and the map downloaded from Illumina website. Matt's map is more inforamtive. It contains less SNPs (N=37,568) but more of them have physical information. However, the top/bot allele issue need to be first addressed.

```{r, eval=FALSE}
### output top/bot allele with the chr and pos info pulled out from Matt's data.
source("../profiling/1.Introgression/1.A.1_snps_topbot.R")
```

# Transform top/bot to forward strand

Use the perl code **top2ref** from __zmSNPtools__ to do the trick. Here is how I did it:

```{r, eval=FALSE}
### install the software
export PERL5LIB=$PERL5LIB:~/Documents/Github/zmSNPtools/modules
cp packages/top2ref/top2ref.pl bin/top2ref
chmod +x bin/top2ref

### use samtools to index reference genome in fasta format
sed -i -- 's/chromosome:AGPv2:.*chromosome /chr/g' ZmB73_RefGen_v2.fasta
samtools faidx ZmB73_RefGen_v2.fasta

### run the program to determine the strand first
cd /home/jolyang/Documents/Github/N2/largedata
cat snp50k_topbot.txt | top2ref -r ~/dbcenter/AGP/AGPv2/ZmB73_RefGen_v2.fasta > snp50k_topbot.map

### remove SNPs that could not be determined
source("../profiling/1.Introgression/1.A.2_snp_topbot_remove0.R")
# only 11 SNPs could not be determined, that is acceptable

### run the program again to flip the 37k SNPs
cat snp50k_topbot.txt | top2ref -m snp50k_topbot.map > snp50k_topbot.fwd

```

# Translate top/bot to ref/alt

Assemble all the information together with teh __"top/bot"__, __"fwdtop/fwdbot"__ and __"ref/alt"__ alleles information. These could be used as the translation table, where top=>fwdtop, bot=>fwdbot.  

```{r, eval=FALSE}
### generate the translation table
source("../profiling/1.Introgression/1.A.3_snp_translation_table.R")
```


# Phasing parental reference populations using __fastPHASE__

Run the following `R` script to format the SNP50k data and the formatted data were used as the `fastPHASE`[^r1] input. The formatted data included:  
1. Mexicana (N=120)  
2. Parviglumis (N=130)  
3. Landraces (N=94)   

```{r, eval=FALSE}
source("profiling/1.Introgression/1.A.1_fastPHASE_input.R")
```
And then run `fastPHASE` to do the haplotype phasing with [HMM](http://statweb.stanford.edu/~nzhang/Stat366/Lecture5.pdf). Basically, I ran the code, for example  
`fastPHASE -oMex -S1234 mex_120.fp`,   
to do the hap phasing. To run on `farm` with `slurm`, I prepared the slurm codes with an `R` script. 
```{r eval=FALSE}
source("../profiling/1.Introgression/1.A.2_run_fastPHASE.R")

# run the following code on farm
```
```
cd /home/jolyang/Documents/Github/Introgression
sbatch -p bigmeml largedata/fphase/mex_fp_slurm.sh
sbatch -p bigmeml largedata/fphase/parv_fp_slurm.sh
sbatch -p bigmeml largedata/fphase/land_fp_slurm.sh
```

# 


[^r1]: Scheet, P., & Stephens, M. (2006). A Fast and Flexible Statistical Model for Large-Scale Population Genotype Data : Applications to Inferring Missing Genotypes and Haplotypic Phase, 78(April), 629–644.


