---
title: "Introgression Analysis"
author: "Jinliang Yang"
date: "Jan. 5th, 2015"
output: rmarkdown::tufte_handout
---

Test whether Totontepec maize lines have admixture with _mexicana_ using SNP50k data. 

# Phasing parental reference populations using __fastPHASE__

Run the following `R` script to format the SNP50k data and the formatted data were used as the `fastPHASE`[^r1] input. The formatted data included:
1. Mexicana (N=120)
2. Parviglumis (N=130)
3. Landraces (N=94)
```{r, eval=FALSE}
source("profiling/1.Introgression/1.A.1_fastPHASE_input.R")
```
And then run `fastPHASE` to do the haplotype phasing with [HMM](http://statweb.stanford.edu/~nzhang/Stat366/Lecture5.pdf). Basically, I ran the code, for example `fastPHASE -oMex -S1234 mex_120.fp`, to do the hap phasing. To run on `farm` with `slurm`, I prepared the slurm codes with an `R` script. 
```{r eval=FALSE}
source("profiling/1.Introgression/1.A.2_run_fastPHASE.R")

# And then run the following code on farm
```
```
cd /home/jolyang/Documents/Github/Introgression
sbatch -p bigmeml largedata/fphase/mex_fp_slurm.sh
sbatch -p bigmeml largedata/fphase/parv_fp_slurm.sh
sbatch -p bigmeml largedata/fphase/land_fp_slurm.sh
```

# 



The phenotypic data _per se_, GCA and SCA was reformatted from Sofiane's files and transformed them to a data matrix. The following chunk of code could not be re-ran because data from external folders were loaded. The original phenotypic data could be found here 
`/group/jrigrp2/DiallelSofiane/GeneticValues/` on `farm`. 

12 Ex-PVP lines are B73, Mo17 and 10 others (LH1, LH123HT, LH82, PH207, 4676A, PHG39, PHG47, PHG84, PHJ40, PHZ51). And the 7 traits of interest are: ASI: anthesis-silk Interval; DTP: days to pollen; DTS: days to silking; EHT: ear height; GY: adjusted grain yield; GY: adjusted grain yield; TW: test weight.




[^r1]: Scheet, P., & Stephens, M. (2006). A Fast and Flexible Statistical Model for Large-Scale Population Genotype Data : Applications to Inferring Missing Genotypes and Haplotypic Phase, 78(April), 629–644.


