---
title: "About SNP Data"
date: 05-16-2017
output: html_notebook
---

#
# Path normalization
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir=normalizePath('../../'))
```

## Early emails:

The first file (`BennettSNPs_FINAL.txt`) includes the first twelve samples Alan sent.  These were samples they extracted in their lab and they did not perform well on the chips (you'll notice there is a lot of missing data).  I do not have any information on the accessions beyond their ID's and you may need to communicate with Pablo to learn more.  The second file (`LandraceSNPs_Final.txt`) is all of the landrace data we included in the landrace cluster file.  This includes your USDA landraces, my introgression landraces, landraces for the centromere project, and the remaining **36 Bennett Samples** (`RIMMA0763-RIMMA0780, RIMMA0782-RIMMA0798`).  There were a total of 49,284 SNPs after clustering (same SNPs in both files on Jeff's site), but there is no missing data cut-off since many projects were included in the cluster.  I've attached more information on the Bennett accessions from the full landrace cluster file.

### Three missing, but only got two from Matt:

- RIHU0001
- RIMMA0786
- RIMMA0787

### merge data to form the final data set

```{r}
library(data.table)
df <- fread("data/LandraceSNPs_FINAL.txt", data.table=FALSE)
names(df)


rif <- read.csv("data/Bennett36_passport.csv")
tonid <- paste0(as.character(rif$RI.Accesssion), ".1")

idx <- which(names(df) %in% tonid)

tonsnp <- df[, c(1, idx)]

m2 <- fread("data/BennettSNPs_Missing2.txt")

d <- merge(tonsnp, m2, by="snpid")
write.table(d, "data/BennettSNP50k_35samples_final.csv", sep=",", row.names=FALSE, quote=FALSE)
```

